Competing Bandits: The Perils of Exploration under Competition

### 2018-09-04 paper/competing_bandits.tex
first pass at another restructure
updates
Commented out "perf-in-iso" which is now obsolete.
Added a macro \Eeod.
Changed \Eeog macro.
more small fixups

\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{url}
\usepackage{graphicx}
\frenchspacing
% Add additional packages here. The following
% packages may NOT be used  (this list
% is not exhaustive:
% authblk, caption, CJK, float, fullpage, geometry,
%hyperref, layout, nameref, natbib, savetrees,
%setspace, titlesec, tocbibind, ulem
%
%US Lettersize Paper Is Required
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
%
%
% PDFINFO
% You are required to complete the following
% for pass-through to the PDF.
% No LaTeX commands of any kind may be
% entered. The parentheses and spaces
% are an integral part of the
% pdfinfo script and must not be removed.
%
\pdfinfo{
/Title  (Competing Bandits: The Perils of Exploration under Competition)
/Author (Guy Aridor, Kevin Liu, Aleksandrs Slivkins, Zhiwei Steven Wu)
/Keywords (Input your keywords in this optional area)
}
%
%Section Numbers
% Uncomment if you want to use section numbers
% and change the 0 to a 1 or 2
 \setcounter{secnumdepth}{2} % section & subsection numbers

@@

\usepackage{amsthm} % The amsthm package provides extended theorem environments
\usepackage{float}
\usepackage{sgame, tikz} % Game theory packages
\usepackage{caption}
\usepackage{algorithm,algpseudocode}
\usepackage{makecell}
 \usepackage{multirow}
 \usepackage{graphicx}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{finding}[definition]{Finding}
\newtheorem{conjecture}[definition]{Conjecture}
\captionsetup{font=footnotesize}

@@

\newcommand{\term}[1]{\ensuremath{\mathtt{#1}}\xspace}
\newcommand{\TS}{\term{TS}}
\newcommand{\DEG}{\term{DEG}}
\newcommand{\DG}{\term{DG}}
\newcommand{\Beta}{\term{Beta}}

@@

% a very useful package for edits and comments, from David Kempe (USC)
\usepackage{color-edits}
%\usepackage[suppress]{color-edits}  % use this to suppress the package
\addauthor{as}{red}    % as for Alex
\addauthor{ga}{blue}  % ga for Guy
\addauthor{sw}{orange} % sw for Steven
% e.g. for Alex, provides \asedit{}, \ascomment{} and \asdelete{}.

@@

\subfile{content/sim_details}

>>>>

\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{url}
\usepackage{graphicx}
\frenchspacing
% Add additional packages here. The following
% packages may NOT be used  (this list
% is not exhaustive:
% authblk, caption, CJK, float, fullpage, geometry,
%hyperref, layout, nameref, natbib, savetrees,
%setspace, titlesec, tocbibind, ulem
%
%US Lettersize Paper Is Required
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
%
%
% PDFINFO
% You are required to complete the following
% for pass-through to the PDF.
% No LaTeX commands of any kind may be
% entered. The parentheses and spaces
% are an integral part of the
% pdfinfo script and must not be removed.
%
\pdfinfo{
/Title  (Competing Bandits: The Perils of Exploration under Competition)
/Author (...)
/Keywords (Input your keywords in this optional area)
}
%
%Section Numbers
% Uncomment if you want to use section numbers
% and change the 0 to a 1 or 2
 \setcounter{secnumdepth}{2} % section & subsection numbers

@@

\usepackage{amsthm} % The amsthm package provides extended theorem environments
\usepackage{float}
\usepackage{sgame, tikz} % Game theory packages
\usepackage{caption}
\usepackage{algorithm,algpseudocode}
\usepackage{makecell}
 \usepackage{multirow}
 \usepackage{graphicx}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{finding}{Finding}
\newtheorem{conjecture}{Conjecture}
\newtheorem{puzzle}{Puzzle}
\captionsetup{font=footnotesize}

@@

\newcommand{\term}[1]{\ensuremath{\mathtt{#1}}\xspace}
\newcommand{\TS}{\term{TS}}
\newcommand{\DEG}{\term{DEG}}
\newcommand{\DG}{\term{DG}}
\newcommand{\Beta}{\term{Beta}} % for Beta distribution
\newcommand{\Eeog}{\term{EoG}} % shorthand for "effective end of game"

@@

% a very useful package for edits and comments, from David Kempe (USC)
\usepackage{color-edits}
%\usepackage[suppress]{color-edits}  % use this to suppress the package
\addauthor{as}{red}    % as for Alex
\addauthor{ga}{blue}  % ga for Guy
\addauthor{sw}{orange} % sw for Steven
% e.g. for Alex, provides \asedit{}, \ascomment{} and \asdelete{}.
\setlength{\tabcolsep}{8pt} % Default value: 6pt
\renewcommand{\arraystretch}{1.5} % Default value: 1

@@

%\subfile{content/sim_details}

### 2018-09-04 paper/content/inverted_u.tex
more small fixups

\xhdr{Permanent Duopoly} \swedit{Since both firms enter at the same time, they will both get an expected market share of $1/2$ whenever they deploy
  the same algorithms. We will mainly investigate the market shares
  when the firms play different algorithms.  In Tables \ref{sim_ht}
  and \ref{sim_nih}, we report the average market share taken over the
  $N$ simulations for different values of warm-up length $T_0$, and
  also the mean and median of the EEOG, under heavy tail and needle in
  haystack instances.}

@@

% latex table generated in R 3.4.0 by xtable 1.8-2 package
% Thu Aug 16 13:13:01 2018
\begin{table*}[h]
\centering
\begin{tabular}{|c|c|c|c||c|c|c|}
  \hline
  & \multicolumn{3}{c|}{Heavy-Tail} 
  & \multicolumn{3}{c|}{Needle-in-Haystack}\\
  \hline 
  & $T_0$ = 20 & $T_0$ = 250 & $T_0$ = 500 
  & $T_0$ = 20 & $T_0$ = 250 & $T_0$ = 500 \\
  \hline
\TS vs \DG 
  & \makecell{\textbf{0.29} $\pm$0.03\\ \Eeog 55 (0)} 
  & \makecell{\textbf{0.72} $\pm$0.02\\ \Eeog 570 (0)} 
  & \makecell{\textbf{0.76} $\pm$0.02\\ \Eeog 620 (99)} 
  %%
  & \makecell{\textbf{0.64} $\pm$0.03\\ \Eeog 200 (27)}
  & \makecell{\textbf{0.6} $\pm$0.03\\ \Eeog 370 (0}
  & \makecell{\textbf{0.64} $\pm$0.03\\ \Eeog 580 (122)}
  \\
\hline
  $\TS$ vs $\DEG$ 
  & \makecell{\textbf{0.3} $\pm$0.03\\ \Eeog 37 (0)} 
  & \makecell{\textbf{0.88} $\pm$0.01\\ \Eeog 480 (0)}
  & \makecell{\textbf{0.9} $\pm$0.01\\ \Eeog 570 (114)} 
  %%
  & \makecell{\textbf{0.57} $\pm$0.03\\ \Eeog 150 (14}
  & \makecell{\textbf{0.52} $\pm$0.03\\ \Eeog 460 (79)}
  & \makecell{\textbf{0.56} $\pm$0.02\\ \Eeog 740 (628)} 
  \\
\hline
  $\DG$ vs $\DEG$ 
  & \makecell{\textbf{0.62} $\pm$0.03\\ \Eeog 410 (7)}
  & \makecell{\textbf{0.6} $\pm$0.02\\ \Eeog 790 (762)}
  & \makecell{\textbf{0.57} $\pm$0.03\\ \Eeog 730 (608)} 
  %%
  & \makecell{\textbf{0.46} $\pm$0.03\\ \Eeog 340 (129)}
  & \makecell{\textbf{0.42} $\pm$0.02\\ \Eeog 650 (408)}
  & \makecell{\textbf{0.42} $\pm$0.02\\ \Eeog 690 (467)} 
  \\
   \hline
\end{tabular}
\caption{The duopoly experiment for Uniform and Needle-in-Haystack instances. Each cell describes a game between two algorithms, call them Alg1 vs. Alg2, for a particular value of the warm start $T_0$. The first line in the cell is the market share of Alg 1: the average (in bold) and the 95\% confidence band.
%For example, the cell in the top left indicates that TS gets on average 64\% of the market when played against DG. 
The second line specifies the ``effective end of game" (\Eeog): the average and the median (in brackets).}
\label{sim_ht}
\end{table*}

>>>>

% latex table generated in R 3.4.0 by xtable 1.8-2 package
% Thu Aug 16 13:13:01 2018
\begin{table*}[h]
\centering
\begin{tabular}{|c|c|c|c||c|c|c|}
  \hline
  & \multicolumn{3}{c|}{Heavy-Tail} 
  & \multicolumn{3}{c|}{Needle-in-Haystack}\\
  \hline 
  & $T_0$ = 20 & $T_0$ = 250 & $T_0$ = 500 
  & $T_0$ = 20 & $T_0$ = 250 & $T_0$ = 500 \\
  \hline
\TS vs \DG 
  & \makecell{\textbf{0.29} $\pm$0.03\\ \Eeog 55 (0)} 
  & \makecell{\textbf{0.72} $\pm$0.02\\ \Eeog 570 (0)} 
  & \makecell{\textbf{0.76} $\pm$0.02\\ \Eeog 620 (99)} 
  %%
  & \makecell{\textbf{0.64} $\pm$0.03\\ \Eeog 200 (27)}
  & \makecell{\textbf{0.6} $\pm$0.03\\ \Eeog 370 (0}
  & \makecell{\textbf{0.64} $\pm$0.03\\ \Eeog 580 (122)}
  \\
\hline
  $\TS$ vs $\DEG$ 
  & \makecell{\textbf{0.3} $\pm$0.03\\ \Eeog 37 (0)} 
  & \makecell{\textbf{0.88} $\pm$0.01\\ \Eeog 480 (0)}
  & \makecell{\textbf{0.9} $\pm$0.01\\ \Eeog 570 (114)} 
  %%
  & \makecell{\textbf{0.57} $\pm$0.03\\ \Eeog 150 (14}
  & \makecell{\textbf{0.52} $\pm$0.03\\ \Eeog 460 (79)}
  & \makecell{\textbf{0.56} $\pm$0.02\\ \Eeog 740 (628)} 
  \\
\hline
  $\DG$ vs $\DEG$ 
  & \makecell{\textbf{0.62} $\pm$0.03\\ \Eeog 410 (7)}
  & \makecell{\textbf{0.6} $\pm$0.02\\ \Eeog 790 (762)}
  & \makecell{\textbf{0.57} $\pm$0.03\\ \Eeog 730 (608)} 
  %%
  & \makecell{\textbf{0.46} $\pm$0.03\\ \Eeog 340 (129)}
  & \makecell{\textbf{0.42} $\pm$0.02\\ \Eeog 650 (408)}
  & \makecell{\textbf{0.42} $\pm$0.02\\ \Eeog 690 (467)} 
  \\
   \hline
\end{tabular}
\caption{The duopoly experiment for Uniform and Needle-in-Haystack instances. Each cell describes a game between two algorithms, call them Alg1 vs. Alg2, for a particular value of the warm start $T_0$. The first line in the cell is the market share of Alg 1: the average (in bold) and the 95\% confidence band.
%For example, the cell in the top left indicates that TS gets on average 64\% of the market when played against DG. 
The second line specifies the ``effective end of game" (\Eeog): the average and the median (in brackets).}
\label{sim_table}
\end{table*}
\xhdr{Permanent Duopoly} \swedit{Since both firms enter at the same time, they will both get an expected market share of $1/2$ whenever they deploy
  the same algorithms. We will mainly investigate the market shares
  when the firms play different algorithms.  In Table \ref{sim_table}, we report the average market share taken over the
  $N$ simulations for different values of warm-up length $T_0$, and
  also the mean and median of the EEOG, under heavy tail and needle in
  haystack instances.}

@@
